Flowchart of Current Algorithm

### 2012-07-18 docs/flowchart/flowchart.tex
more notes about initialization
add a section label

@@

First, we need to construct approximations to $S^0, w_0^{-\myhalf}, \Delta t^0$, 
and $\Ub^0$.  Start with initial data $X_k^{\initp}, \rho^{\initp},$ $T^{\initp},$ an 
initial base state, and an initial guess for the velocity, $\Ub^{\initp}$.
Set $w_0^0 = 0$ as an initial approximation.  Use the equation of state to 
determine $(\rho h)^{\initp}$.  Compute $\beta_0^0$ as a function of 
the initial data.  Then, project $\Ub^{\initp}$ using $\beta_0^0$ and 
$S = \rho\Hext$, giving $\Ub^{0,0}$.  The next part of the initialization process 
proceeds as follows.

@@

\item {\em Initial Projection}: if {\tt do\_initial\_projection = T}, then we 
   first project the velocity field with $\rho = 1$ and $\beta_0^0$ defined 
   from the initial data.  No sources are included in $S$.  The elliptic
   equation we solve is 
   \begin{equation}
   \nabla \cdot \beta_0^0 \nabla \phi = - \nabla \cdot (\beta_0^0 \Ub^0)
   \end{equation}
   This $\phi$ is then used to correct the velocity field.

\item {\em ``Divu'' iterations}: Next we do {\tt init\_divu\_iter} iterations 
  to project the velocity field using a constraint that sees the reactions. 
  The initial timestep estimate is provided by {\tt firstdt}, to allow us to 
  integrate the reaction networks.  In this projection, again the density is 
  set to 1, and the elliptic equation we solve is:
   \begin{equation}
   \nabla \cdot \beta_0^0 \nabla \phi = \beta_0 (S - \Sbar)- \nabla \cdot (\beta_0^0 \Ub^0)
   \end{equation}

@@

  \item Project $\Ub^{0,\nu-1}$ using $\beta_0^0$ and 
        $(S^{0,\nu} - \overline{S^{0,\nu}})$ as the source term.  
        This yields $\Ub^{0,\nu}.$

@@

>>>>

\label{sec:flow:initialization}

@@

First, we need to construct approximations to $S^0, w_0^{-\myhalf}, \Delta t^0$, 
and $\Ub^0$.  Start with initial data $X_k^{\initp}, \rho^{\initp},$ $T^{\initp},$ 
an initial base state, and an initial guess for the velocity, $\Ub^{\initp}$.
Set $w_0^0 = 0$ as an initial approximation.  Use the equation of state to 
determine $(\rho h)^{\initp}$.  Compute $\beta_0^0$ as a function of 
the initial data.  The next part of the initialization process 
proceeds as follows.

@@

\item {\em Initial Projection}: if {\tt do\_initial\_projection = T}, then we 
   first project the velocity field with $\rho = 1$ and $\beta_0^0$.
   The initial projection does not see reactions
   or external heating, and thus we set $\dot\omega = \Hnuc = \Hext = 0$ in $S$.
   The reason for ignoring reactions and heating is that we need some kind of 
   time scale over which to compute the effect of reactions, but we first 
   need an estimate of the velocity
   field in order to derive the time step that will be used as a time scale.
   The elliptic equation we solve is 
   \begin{equation}
   \nabla \cdot \beta_0^0 \nabla \phi = \beta_0^0(S - \Sbar)- \nabla \cdot (\beta_0^0 \Ub^{\initp})
   \end{equation}
   This $\phi$ is then used to correct the velocity field to obtain $\Ub^{0,0}$.
   If {\tt do\_initial\_projection = F}, set $\Ub^{0,0} = \Ub^{\initp}$.

\item {\em ``Divu'' iterations}: Next we do {\tt init\_divu\_iter} iterations 
  to project the velocity field using a constraint that sees reactions
  and external heating. 
  The initial timestep estimate is provided by {\tt firstdt} and
  $\Ub^{0,0}$, to allow us to compute the effect of reactions over $\Delta t/2$.

@@

  \item Project $\Ub^{0,\nu-1}$ using $\beta_0^0$ and 
        $(S^{0,\nu} - \overline{S^{0,\nu}})$ as the source term.  
        This yields $\Ub^{0,\nu}.$  In this projection, again the density is 
        set to 1, and the elliptic equation we solve is:

   \begin{equation}
   \nabla \cdot \beta_0^0 \nabla \phi = \beta_0 (S - \Sbar)- \nabla \cdot (\beta_0^0 \Ub^{0,\nu-1})
   \end{equation}

@@

The tolerances for these elliptic solves are described in \S~\ref{sec:mgtol}.
